---
title: "Workflow for fitting SCENIC using ZIRFs-derived variable importance measures (VIMs)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{zirfsSCENICvignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We first need to load the required packages to run SCENIC with ZIRFs variable importance measures
(VIMs). For guidance on downloading the requisite packages to use SCENIC see SCENIC's
documentation on installation and set-up:
https://github.com/aertslab/SCENIC/blob/master/vignettes/SCENIC_Setup.Rmd.
```{r setup}
suppressPackageStartupMessages({
  library(scRNAzirf)
  library(SCENIC)
  library(foreach)
})
knitr::opts_knit$set(root.dir="zirfsSCENIC_vignette") 
```

We will go through a toy example using diaphragm cell data from the Tabula Muris Consortium
(https://tabula-muris.ds.czbiohub.org/). During this vignette we will be downloading databases,
creating intermediate files, and output files. We recommend creating new directories to keep
these files organized.

## Directories
```{r dirsetup, eval = FALSE}
#directory which we will be primarily working in
dir.create("zirfsSCENIC_vignette")
setwd("zirfsSCENIC_vignette")
#directory where databases for motif scoring in SCENIC will be held
dir.create("mousedb")
```


To run this example you'll need to download the following data sets which allow motifs to be 
scored in SCENIC:
dbFiles <- c("https://resources.aertslab.org/cistarget/databases/mus_musculus/mm9/refseq_r45/mc9nr/gene_based/mm9-500bp-upstream-7species.mc9nr.feather",
"https://resources.aertslab.org/cistarget/databases/mus_musculus/mm9/refseq_r45/mc9nr/gene_based/mm9-tss-centered-10kb-7species.mc9nr.feather")
These files can be downloaded using either curl or wget.
For example using curl would look as follows: 
curl https://resources.aertslab.org/cistarget/databases/mus_musculus/mm9/refseq_r45/mc9nr/gene_based/mm9-500bp-upstream-7species.mc9nr.feather --output mm9-500bp-upstream-7species.mc9nr.feather
curl https://resources.aertslab.org/cistarget/databases/mus_musculus/mm9/refseq_r45/mc9nr/gene_based/mm9-tss-centered-10kb-7species.mc9nr.feather --output mm9-tss-centered-10kb-7species.mc9nr.feather


We then initialize our SCENIC run. 
```{r}
scenicOptions <- initializeScenic(org = "mgi",
                                  dbDir = "mousedb", dbs = "mousedb", nCores=1)
```

We will then load toy data sets derived from diaphragm cells from the Tabula Muris Consortium.
```{r load_toy_data, eval = TRUE}
data("countDat")
data("normDat")
data("sizeFactors")
data("TF_names")
data("target_names")
```

```{r run_zirf_genie3, eval = TRUE}
#zirf_genie3 <- function(exprMatrix, countMatrix, regulators = NULL, targets = NULL, z,
#                        rounds = 10, mtry = 5, ntree=100, nodesize=5, nlambda=10,
#                        nCores = 1){
zirf_genie3_fit <- zirf_genie3(normDat, countDat, regulators = TF_names,
                               targets = union(target_names, TF_names),
                               z = as.matrix(sizeFactors),
                               nCores = 2)
```

```{r run_SCENIC}
SCENIC_results <- scRNAzirf::run_SCENIC(scenicOptions = scenicOptions,
                                        weightMatrix_list = zirf_genie3_fit,
                                        log_scale = F,
                                        exprMatrix = normDat)
```









